---
title: "NEAR - Comparing the top projects"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    source_code: https://github.com/manuelgirbal/metricsdao/tree/main/11.2022%20-%20NEAR%20-%20Comparing%20The%20Top%20Projects
runtime: shiny
---

<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(shiny)
library(plotly)
library(rsconnect)
```

```{r data, include=FALSE}
options(scipen=999)

data <- read_csv("Data/data.csv")

Variables = c("NEW_USERS", "PRICE", "VOLUME", "MARKET_CAP", "AMOUNT", "TRADERS")
```


Column {.sidebar data-width=200}
-----------------------------------------------------------------------
```{r}
selectInput("Variable", label = "Select variable:", choices = Variables)
```


Column {data-width=400}
-----------------------------------------------------------------------
### Introduction & analysis

Let’s take a closer look at some of the biggest and best-known projects in the NEAR ecosystem.Choose one of the Top projects in the NEAR ecosystem (a list can be found below). Analyze the project and its health. You can include baseline measures, e.g. token price (if applicable), transaction volume, etc., but go beyond that and apply your analysis skills. Choose and define at least 2 measures of ecosystem health, and assess how the project is performing on those metrics. Grand prize winners will also compare the project to at least one other Top NEAR project using the 2 measures provided.

aclarar tablas que usamos (y qué significan), y otras fuentes como Coingecko, además de que lo hicimos vía Shroom_SDK
posible baseline el día que arranca Jumbo
de las tablas queremos tener (como medidas de salud del ecosistema -recordar definirlas metodológicamente-):
 precio -- ok
 volumen de transacciones (solo estables -in swap-) -- ok (también hay volumen Coingecko)
 usuarios diarios -- ok
 nuevos usuarios -- ok

 usamos data de los últimos 6 meses (desde principios de mayo 22)

 El volumen de comercio en 24 horas hace referencia a la cantidad de una criptomoneda 
 que se ha comprado y vendido en todos los intercambios en las últimas 24 horas 
 en el mercado al contado.

 Para el panel con variables interactivas debería tener todo en una sola table

### Ref.finance vs Jumbo

```{r}
renderPlot({
   ggplot(data, aes(x = DATE, y = data[[input$Variable]], color = DEX) ) +
    geom_line() +
    theme_minimal() +
    xlab("Date") +
    ylab("")
})
```





