---
title: "NEAR - Comparing the top projects"
author: manuelgg (@m_i_g_g)
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    source_code: https://github.com/manuelgirbal/metricsdao/tree/main/11.2022%20-%20NEAR%20-%20Comparing%20The%20Top%20Projects
runtime: shiny
---

<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(shiny)
library(plotly)
library(rsconnect)
```

```{r data, include=FALSE}
options(scipen=999)

data <- read_csv("Data/data.csv")

Variables = c("NEW_USERS", "PRICE", "AMOUNT", "TRADERS")
```


Column {.sidebar data-width=250}
-----------------------------------------------------------------------
```{r}
selectInput("Variable", label = h3("Data:"), choices = Variables)
```

Data was queried from [Flipside Crypto](https://flipsidecrypto.xyz/) and [Coingecko](https://www.coingecko.com/) using their APIs (see code for more detail).

- **AMOUNT***: amount of daily USD value used for swapping inside the DEX. 
- **NEW_USERS***: amount of daily new users that swapped inside the DEX.
- **TRADERS***: amount of daily users that swapped inside the DEX.
- **PRICE**: evolution of the DEX native token price in USD value.

*_For these variables only swaps done with stablecoins (DAI, USN, USDT & USDC) were considered._

Column {data-width=400}
-----------------------------------------------------------------------
### Introduction

Let’s take a closer look at some of the biggest and best-known projects in the NEAR ecosystem.
In this dashboard, we we'll be comparing two of NEAR's most known decentralized exchanges: [Ref.finance](https://www.ref.finance/) and [Jumbo](https://jumbo.exchange/).

The 4 metrics chosen to compare each project's health since May 22 are described on the side bar, where you'll be able to choose which comparison variable you'd like to see.


### Ref.finance vs Jumbo

```{r}
renderPlot({
   ggplot(data, aes(x = DATE, y = data[[input$Variable]], color = DEX) ) +
    geom_line(size=1) +
    theme_minimal() +
    xlab("Date") +
    ylab("") +
    scale_x_date(date_breaks = "1 month", date_labels = "%m-%Y")
})
```

### Key insights

- Amount of value transacted on Ref is way more significant than on Jumbo, but it saw better days on May 22 than now.
- Daily users and new users is also bigger in Ref (the amount of daily new users on Jumbo is close to 0 in many of those days). These variables remained more or less stable during the last six months (it doesn't appear to be a decline on both DEXes usage).
- Both token prices are declining (not a big surprise in this bear market), but $REF might be stabilizing. 

Overall, Ref is more used than Jumbo as regards to trading with stablecoins, but this might be also due to the first one being an older project than the latter. 



